Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie negative examples. Breaking rules are specified 
using disjunctions.

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
   \draw[help lines]
    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
  \end{tikzpicture}
  \caption{System architecture of }
  \label{fig:versionSL}
\end{figure}

Necessary = 
 { Keyword, value pair "language:node_js" requires Keyword "node_js"}

where keyword "node_js" sets a version value (e.g. "node_js: 0.8")

Breaking =
  { Keyword "node_js" cannot have value <= 0 }

>>>>

Figure~\ref{fig:versionSL} outlines our proposed approach. We first apply the standard \app's approach to learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie~negative examples. Breaking rules are specified 
using disjunctions.

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (6,4); 
    \node [align=left] at (1.5,3.2) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
    \draw (1.5,0.2) rectangle (5,2.2);
    \node [align=left] at (3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
  \label{fig:versionSL}
\end{figure}
